Merging Datasets Through Deep learning

### 2018-08-31 paper2018/evaluation.tex
adding references to face datasets

 We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.  To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2, and CasiaWebFace.  We took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set at \url{http://vis-www.cs.umass.edu/lfw/} using these embeddings.  We put these output embeddings into an ANN structure, and computed our metrics on that.  Recall of the same face was remarkably similar to our results for names, getting 80\% on the VGGFace2 dataset, and 76\% for the Casia Web Face dataset.  However, we found precision at one was much lower on both datasets at 23\% for VGGFace2 and 21\% for Casia Web faces.

>>>>

 We have demonstrated that our strategy for joins could work well for textual names of people and companies, but the technique could potentially work for any kind of data for which a vector embedding can be made.  To test how well that works, we evaluated two existing models for face recognition that were trained with the same approaches defined in the \cite{DBLP:conf/cvpr/SchroffKP15} on two different datasets, VGGFace2 \cite{DBLP:conf/fgr/CaoSXPZ18}, and CasiaWebFace \cite{DBLP:conf/cvpr/SchroffKP15}.  We took the existing trained model at \url{https://github.com/davidsandberg/facenet}, and extracted the output embeddings for faces from the LFW test set \cite{Huang2012a} using these embeddings.  We put these output embeddings into an ANN structure, and computed our metrics on that.  Recall of the same face was remarkably similar to our results for names, getting 80\% on the VGGFace2 dataset, and 76\% for the Casia Web Face dataset.  However, we found precision at one was much lower on both datasets at 23\% for VGGFace2 and 21\% for Casia Web faces.
